### 2017-04-06 paper/evaluation.tex
answering comments

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases\Mar{note that one is a case of very high speedup and
  another is a case of very high slowdown.  It is strange that the
  same explanation justify both cases.  Are you only referring to
  Log4J2 or both cases in your explanation?}: \CodeIn{Jcabi} and \CodeIn{Log4J2}, which most test
classes run one, two, or three test methods with the configuration
\Mar{We are not using bold for these.  If you want you can change, but
  please do so by holding all locks.}\textbf{C2}, without the
reutilization of JVM forks\Mar{Don't understand.
  Fork-configurations have an F in front, no?  Like FC1.  Please
  check.  Do you mean FC0 for Log4J? (I checked Figure 10)}. This specific
configuration is useful when there is the need to isolate the test
class execution from another, which is the case.
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

@@

\Luis{Pie chart}

>>>>

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases: \CodeIn{Jcabi} and \CodeIn{Log4J2}.
The first when using the default parallel configuration, runs a
\textbf{C3} configuration with small test classes and big test
methods, allowing to run multiple methods and classes at once. The
high slowdown happens when big methods run sequentially.
\Comment{The second which most test
classes run one, two, or three test methods with the configuration
\Mar{We are not using bold for these.  If you want you can change, but
  please do so by holding all locks.}\textbf{C2}, without the
reutilization of JVM forks\Mar{Don't understand.
  Fork-configurations have an F in front, no?  Like FC1.  Please
  check.  Do you mean FC0 for Log4J? (I checked Figure 10)}. This specific
configuration is useful when there is the need to isolate the test
class execution from another, which is the case.}
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/survey.pdf}                                                                                                                                                   
     \caption{\Luis{todo}}
\end{figure}
